A Typed Programmatic Interface to Contracts on the Blockchain

### 2021-02-18 papers/execution-model/model.tex
Add files via upload
section-3

\section{Execution Model}
\label{sec:execution-model}

>>>>

\section{Execution Model}
\label{sec:execution-model}
The context of our work is the Tezos blockchain \cite{tezos-whitepaper, tezos-intropaper}. Tezos is a self-amending blockchain that improves several aspects compared to established 
blockchains. Tezos introduces an original consensus algorithm called Liquid Proof of Stake that allows consensus not only on the state of its ledger, like Bitcoin \cite{bitcoin-whitepaper} or Ethereum \cite{eth-whitepaper}, but also on how the economic protocol and the nodes should  upgrade, and serves as a decentralized smart contract platform that focuses on formal methods to improve security.

In Tezos, there are two types of accounts: implicit accounts and smart contracts, and they are stateful. An implicit account is a non-programmable account and is associated with a pair of private/public keys. A smart contract is a programmable account created by an origination operation and has no corresponding secret key. The address of a smart contract is a unique public hash that depends on the creation operation. All existing accounts are stored in a context component on the blockchain. An implicit account is managed with its public key, balance, and counter, whose job is to prevent replay attacks. A smart contract account is stored with its script, storage, and balance. Tezos provides the Michelson language for writing a smart contract. Michelson is a stack-based language with strict static type checking. A contract is a function that maps a pair of a parameter and a storage, which have fixed and monomorphic types to a pair of a list of internal operations and an updated storage. The script of a smart contract must be type-checked before it is introduced into the system.

An implicit account can perform three kinds of transactions: (1) transfer tokens to another implicit account, (2) transfer (invoke) a smart contract, or (3) originate a new smart contract.E ach transaction includes the address of the sender contract, the address of the destination contract, the amount of tokens transferred, and a fee to be paid either by payment to a baker or by destruction (burning). In addition, a smart contract invocation must provide input data and and an origination transaction specifies the script of the contract and the initial content of the contract storage.  A transaction can only be sent if it has been signed with the sender contract's private key. It is then injected into the blockchain network via a node that runs the gossip network and updates the context. The node first validates the transaction before submitting it to the network. In general, a transaction can fail for a number of reasons, including incorrect destination address, insufficient balances, incorrect counters, and incorrect type of input parameters (or scripts). A transaction is valid only if the counter of the sender contract is the same as the counter  used in the transaction. The invocation of a smart contract may fail for reasons determined by the contract's script. An invalid transaction is rejected by the node.

Once the transaction is valid, it is injected into the mempool, which contains all pending transactions before they can be included in a block. On the other hand, a pending transaction may get lost in the mempool. That is, it may be dropped. There are several
causes for dropping, primarily timeout or overflow of the mempool, which is limited in size in the implementation. A transaction is timed out when 60 blocks have passed and it can no longer be included in a block. When a transaction is included in a blockchain, the amount of tokens transferred is added to the balance of destination contract and when a smart contract call is made, the script of the destination contract is executed. Once a transaction is applied, the counter increments by one, preventing the transaction from being reused.
